---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tools42

<!-- badges: start -->
<!-- badges: end -->

The goal of tools42 is to make life easier for folks at ideas42 who are doing analytical work. While this is a work in progress, our goal is to include features like:

- Simple plotting functions for exploratory data analysis using `ggplot2`
- Helper functions for data cleaning, wrangling, and analysis
- Templates for projects, reports, and briefs
- Themes for publication-ready figures
- Functions to help you export data and results in accessible formats

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ideas42/tools42")
```
## Example: plots

This is a basic example which shows you how to solve a common problem: plotting a histogram.

```{r example, dpi=300}

library(tools42)
## basic example code

viz_hist(iris, "Sepal.Width")

```

## Example: themes

Let's try using our theme now:

```{r example2, dpi=300}
library(ggplot2)

ggplot(iris, aes(Sepal.Width, Sepal.Length)) + 
  geom_point() +
  labs(title = "This is a sample plot",
       subtitle = "And this is the subtitle") +
  theme_42()

```

```{r example2b, dpi=300}

ggplot(iris, aes(Sepal.Width, Sepal.Length)) + 
  geom_point() +
  labs(title = "This is a sample plot",
       subtitle = "And this is the subtitle") +
  theme_42_bright()

```

## Example: palettes 

Now, let's color it with one of our palettes. First we can take a look at the palette separately.

```{r example3, dpi=300, fig.asp=0.4}

palette_42("i42")

```

Then we plot the same chart and add our colors.

```{r example4, dpi=300}

ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) + 
  geom_point() +
  labs(title = "This is a sample plot",
       subtitle = "And this is the subtitle") +
  theme_42_bright() +
  scale_color_manual(values = palette_42("i42_bright"))

```


